### 2010-09-27 Documentation/part1.tex

In some cases, it is necessary to obtain information from the loaded \AEDL\
files. This and the next sections are marked as advanced because knowledge of \AEDL\ is
required, \ie,  the reader should be familiar with Part~\ref{part:2} of the manual.
%
Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin}, {\tt emax}] covered by the binning as defined in the \AEDL\ file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low}, {\tt high}] defined in the \AEDL\ file for the experiment
{\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin}, {\tt highbin}] corresponding to the energy window defined in the \AEDL\ file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

In order to obtain information on the structure of the rules, 
a number of functions are provided:
\begin{function}
\GLBNS{GetNumberOfRules}
{\tt int glbGetNumberOfRules(int exp)} returns the number of
rules in experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetLengthOfRule}
{\tt int glbGetLengthOfRule(int exp, int rule, int signal)} returns
the length of rule {\tt rule} in experiment {\tt exp}. The parameter
{\tt signal} can be either \GLBC{GLB\_SIG} for the number of signal
components or \GLBC{GLB\_BG} for the number of background components.
\end{function}
% NOT DOCUMENTED, BECAUSE THESE NORMALIZATIONS ARE NOW PRE-DEFINED:
%
% \begin{function}
% \GLBNS{GetNormalizationInRule}
% {\tt double glbGetNormalizationInRule(int exp, int rule, int signal)}
% returns the normalization (normalization or background center)
% in rule {\tt rule} of the experiment {\tt exp}.
% The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
% (\GLBC{GLB\_BG}).
% \end{function}
\begin{function}
\GLBNS{GetChannelInRule}
{\tt int glbGetChannelInRule(int exp, int rule, int pos, int signal)}
returns the channel number in rule {\tt rule} at the position {\tt pos}
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}).
\end{function}
\begin{function}
\GLBNS{GetCoefficientInRule}
{\tt double glbGetCoefficientInRule(int exp, int rule, int pos, int signal)}
returns the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}).
\end{function}
%
Similarly to the rules, one can find the number of channels of an experiment:
\begin{function}
\GLBNS{GetNumberOfChannels}
{\tt int glbGetNumberOfChannels(int exp)} returns the number of 
channels of experiment {\tt exp}.
\end{function} 
For each channel, the efficiencies and backgrounds can be returned with the following functions:
\begin{function}
\GLBNS{GetEfficiencyPtr}
{\tt double *glbGetEfficiencyPtr(int exp, int ch, int pre\_post)} returns a pointer to
the efficiency list for experiment {\tt exp} and channel {\tt ch}. The pre- or post-smearing
efficiencies are returned with {\tt pre\_post} set to {\tt GLB\_PRE} and {\tt GLB\_POST}, respectively.
\end{function}
\begin{function}
\GLBNS{GetBackgroundPtr}
{\tt double *glbGetBackgroundPtr(int exp, int ch, int pre\_post)} returns a pointer to
the background list for experiment {\tt exp} and channel {\tt ch}. The pre- or post-smearing
backgrounds are returned with {\tt pre\_post} set to {\tt GLB\_PRE} and {\tt GLB\_POST}, respectively.
\end{function}

@@

\index{norm}{Signal!errors}
\index{norm}{Background!errors}
\index{norm}{Background!centers}
Except from the general treatment of systematics, one can read out
and change the signal and background errors for standard pre-defined systematics
during running time:
\begin{function}
\GLBNS{SetSignalErrors}
{\tt int glbSetSignalErrors(int exp, int rule, double norm, double tilt)}
sets the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetSignalErrors}
{\tt int glbGetSignalErrors(int exp, int rule, double* norm, double* tilt)}
writes the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{SetBGErrors}
{\tt int glbSetBGErrors(int exp, int rule, double norm, double tilt)}
sets the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetBGErrors}
{\tt int glbGetBGErrors(int exp, int rule, double* norm, double* tilt)}
writes the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
% ELIMINATED FROM DOC, BECAUSE WE WANT TO AVOID THE BG CENTERS IN THE FUTURE (CONFUSION) [WW]
%
% \begin{function}
% \GLBNS{SetBGCenters}
% {\tt int glbSetBGCenters(int exp, int rule, double norm, double tilt)}
% sets the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
% \begin{function}
% \GLBNS{GetBGCenters}
% {\tt int glbGetBGCenters(int exp, int rule, double* norm, double* tilt)}
% writes the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
As a more flexible concept, the systematical errors may be given as lists for
both user-defined and built-in systematics. For example, the standard signal and background
pre-defined errors can be accessed as lists with four elements (signal
normalization, signal tilt, background normalization, background tilt) if built-in
systematics is used. The corresponding 
functions are:
\begin{function}
\GLBNS{SetSysErrorsList} 
{\tt int glbSetSysErrorsList(int exp, int rule, int on\_off, const double *sys\_list)}
changes the systematical errors defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule} to the values in {\tt sys\_list}. This change can be perfomed for
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
\begin{function}
\GLBNS{GetSysErrorsListPtr} 
{\tt double* glbGetSysErrorsListPtr(int exp, int rule, int on\_off)}
returns a pointer to the list of systematical errors as defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule}. Choose
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
As usual, all these functions return $-1$ if they were not successful.
%.
For user-defined systematics, see \Sec~\ref{sec:userchi}, and 
for the definitions of these quantities, see \Sec~\ref{sec:rules}.

@@

In order to use the user-defined variable, one has to assign it 
with {\tt glbDefineAEDLVariable} {\em before} the experiment is initialized with \GLB{InitExperiment}:
\begin{function}
\GLBNS{DefineAEDLVariable}
{\tt void glbDefineAEDLVariable(const char* name, double value)}
assigns the value {\tt value} to the \AEDL\ variable {\tt name}.
\end{function}
In our energy resolution example, one could now loop over the
energy resolution such as with
\begin{quote}
{\tt
int i; \\
for(i=5;i<20;i++) \\
\{ \\    
\hspace*{1cm} glbClearExperimentList(); \\
\hspace*{1cm} glbDefineAEDLVariable("myres",0.01*i); \\
\hspace*{1cm} glbInitExperiment(...); \\
\\
\hspace*{1cm} /* do something */ \\
\}
}
\end{quote}
Note that one does not have to re-initialize the oscillation
parameter vectors every time within the loop as long as the
number of experiments does not change.

>>>>

In some cases, it is necessary to obtain information from the loaded \AEDL\
files. This and the next sections are marked as advanced because knowledge of \AEDL\ is
required, \ie,  the reader should be familiar with Part~\ref{part:2} of the manual.
%
Very basic information is supplied with
\begin{function}
\GLBNS{GetEminEmax}
{\tt int glbGetEminEmax(int experiment, double *emin, double *emax)} returns the
energy range [{\tt emin}, {\tt emax}] covered by the binning as defined in the \AEDL\ file for the experiment
{\tt experiment}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindow} \label{glbGetEnergyWindow}
{\tt int glbGetEnergyWindow(int exp, int rule, double *low, double *high)} returns the
energy window [{\tt low}, {\tt high}] defined in the \AEDL\ file for the experiment
{\tt exp} and rule {\tt rule}. See also {\tt glbSetEnergyWindow} on page~\pageref{glbSetEnergyWindow}.
\end{function}
\begin{function}
\GLBNS{GetEnergyWindowBins}
{\tt int glbGetEnergyWindowBins(int exp, int rule, int *lowbin, int *highbin)} returns the
energy window in terms of bin numbers [{\tt lowbin}, {\tt highbin}] corresponding to the energy window defined in the \AEDL\ file for the experiment {\tt exp} and rule {\tt rule}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfBins}
{\tt int glbGetNumberOfBins(int exp)} returns the number of bins for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetNumberOfSamplingPoints}
{\tt int glbGetNumberOfSamplingPoints(int exp)} returns the number of sampling points for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinSizeListPtr}
{\tt double *glbGetBinSizeListPtr(int exp)} returns a pointer to the array of bin widths
for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingStepsizeListPtr}
{\tt double *glbGetSamplingStepsizeListPtr(int exp)} returns a pointer to the array of
sampling step sizes for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetBinCentersListPtr}
{\tt double *glbGetBinCentersListPtr(int exp)} returns a pointer to the array of
mean bin energies for the experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetSamplingPointsListPtr}
{\tt double *glbGetSamplingPointsListPtr(int exp)} returns a pointer to the array of
sampling points for the experiment {\tt exp}.
\end{function}

In order to obtain information on the structure of the rules, 
a number of functions are provided:
\begin{function}
\GLBNS{GetNumberOfRules}
{\tt int glbGetNumberOfRules(int exp)} returns the number of
rules in experiment {\tt exp}.
\end{function}
\begin{function}
\GLBNS{GetLengthOfRule}
{\tt int glbGetLengthOfRule(int exp, int rule, int signal)} returns
the length of rule {\tt rule} in experiment {\tt exp}. The parameter
{\tt signal} can be either \GLBC{GLB\_SIG} for the number of signal
components or \GLBC{GLB\_BG} for the number of background components.
\end{function}
% NOT DOCUMENTED, BECAUSE THESE NORMALIZATIONS ARE NOW PRE-DEFINED:
%
% \begin{function}
% \GLBNS{GetNormalizationInRule}
% {\tt double glbGetNormalizationInRule(int exp, int rule, int signal)}
% returns the normalization (normalization or background center)
% in rule {\tt rule} of the experiment {\tt exp}.
% The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
% (\GLBC{GLB\_BG}).
% \end{function}
\begin{function}
\GLBNS{GetChannelInRule}
{\tt int glbGetChannelInRule(int exp, int rule, int pos, int signal)}
returns the channel number in rule {\tt rule} at the position {\tt pos}
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}).
\end{function}
\begin{function}
\GLBNS{GetCoefficientInRule} \label{glbGetCoefficientInRule}
{\tt double glbGetCoefficientInRule(int exp, int rule, int pos, int signal)}
returns the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}). See also {\tt glbSetCoefficientInRule} on page~\pageref{glbSetCoefficientInRule}.
\end{function}
%
Similarly to the rules, one can find the number of channels of an experiment:
\begin{function}
\GLBNS{GetNumberOfChannels}
{\tt int glbGetNumberOfChannels(int exp)} returns the number of 
channels of experiment {\tt exp}.
\end{function} 
For each channel, the efficiencies and backgrounds can be returned with the following functions:
\begin{function}
\GLBNS{GetEfficiencyPtr}
{\tt double *glbGetEfficiencyPtr(int exp, int ch, int pre\_post)} returns a pointer to
the efficiency list for experiment {\tt exp} and channel {\tt ch}. The pre- or post-smearing
efficiencies are returned with {\tt pre\_post} set to {\tt GLB\_PRE} and {\tt GLB\_POST}, respectively.
\end{function}
\begin{function}
\GLBNS{GetBackgroundPtr}
{\tt double *glbGetBackgroundPtr(int exp, int ch, int pre\_post)} returns a pointer to
the background list for experiment {\tt exp} and channel {\tt ch}. The pre- or post-smearing
backgrounds are returned with {\tt pre\_post} set to {\tt GLB\_PRE} and {\tt GLB\_POST}, respectively.
\end{function}

@@

\index{norm}{Signal!errors}
\index{norm}{Background!errors}
\index{norm}{Background!centers}
Except from the general treatment of systematics, one can read out
and change the signal and background errors for standard pre-defined systematics
during running time:
\begin{function}
\GLBNS{SetSignalErrors}
{\tt int glbSetSignalErrors(int exp, int rule, double norm, double tilt)}
sets the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetSignalErrors}
{\tt int glbGetSignalErrors(int exp, int rule, double* norm, double* tilt)}
writes the signal errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{SetBGErrors}
{\tt int glbSetBGErrors(int exp, int rule, double norm, double tilt)}
sets the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
\begin{function}
\GLBNS{GetBGErrors}
{\tt int glbGetBGErrors(int exp, int rule, double* norm, double* tilt)}
writes the background errors of experiment {\tt exp} and rule {\tt rule}
to {\tt norm} (normalization error) and {\tt tilt} (tilt/calibration error).
\end{function}
In addition, the coefficients in the rules can be manipulated by\footnote{Available in GLoBES 3.1.7 and higher.}
\begin{function}
\GLBNS{SetCoefficientInRule} \label{glbSetCoefficientInRule}
{\tt int glbSetCoefficientInRule(int exp, int rule, int pos, int signal, double coeff)}
sets the coefficient of the component {\tt pos} in rule {\tt rule} 
of the experiment {\tt exp} to value {\tt coeff}.
The parameter {\tt signal} refers to signal (\GLBC{GLB\_SIG}) or background
(\GLBC{GLB\_BG}). See also {\tt glbGetCoefficientInRule} on page~\pageref{glbGetCoefficientInRule}.
\end{function}

% ELIMINATED FROM DOC, BECAUSE WE WANT TO AVOID THE BG CENTERS IN THE FUTURE (CONFUSION) [WW]
%
% \begin{function}
% \GLBNS{SetBGCenters}
% {\tt int glbSetBGCenters(int exp, int rule, double norm, double tilt)}
% sets the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
% \begin{function}
% \GLBNS{GetBGCenters}
% {\tt int glbGetBGCenters(int exp, int rule, double* norm, double* tilt)}
% writes the background centers of experiment {\tt exp} and rule {\tt rule}
% to {\tt norm} (normalization center) and {\tt tilt} (tilt/calibration center).
% \end{function}
As a more flexible concept, the systematical errors may be given as lists for
both user-defined and built-in systematics. For example, the standard signal and background
pre-defined errors can be accessed as lists with four elements (signal
normalization, signal tilt, background normalization, background tilt) if built-in
systematics is used. The corresponding 
functions are:
\begin{function}
\GLBNS{SetSysErrorsList} 
{\tt int glbSetSysErrorsList(int exp, int rule, int on\_off, const double *sys\_list)}
changes the systematical errors defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule} to the values in {\tt sys\_list}. This change can be perfomed for
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
\begin{function}
\GLBNS{GetSysErrorsListPtr} 
{\tt double* glbGetSysErrorsListPtr(int exp, int rule, int on\_off)}
returns a pointer to the list of systematical errors as defined in the \AEDL\ file in experiment {\tt exp} and 
rule {\tt rule}. Choose
systematics on or systematics off by using {\tt GLB\_ON} or {\tt GLB\_OFF} for {\tt on\_off}. 
\end{function}
Furthermore, the energy window can be manipulated by\footnote{Available in GLoBES 3.1.7 and higher.}
\begin{function}
\GLBNS{SetEnergyWindow} \label{glbSetEnergyWindow}
{\tt int glbSetEnergyWindow(int experiment, int rule, double low, double high)}
sets the energy window in {\tt experiment} and {\tt rule}, which can be also {\tt GLB\_ALL}. The energy window is limited by the energies {\tt low} and {\tt high}. See also {\tt glbGetEnergyWindow} on page~\pageref{glbGetEnergyWindow}.
\end{function}
As usual, all the set-functions return $-1$ if they were not successful.
%.
For user-defined systematics, see \Sec~\ref{sec:userchi}, and 
for the definitions of these quantities, see \Sec~\ref{sec:rules}.

@@

In order to use the user-defined variable, one has to assign it 
with {\tt glbDefineAEDLVariable} {\em before} the experiment is initialized with \GLB{InitExperiment}:
\begin{function}
\GLBNS{DefineAEDLVariable}
{\tt void glbDefineAEDLVariable(const char* name, double value)}
assigns the value {\tt value} to the \AEDL\ variable {\tt name}.
\end{function}
In our energy resolution example, one could now loop over the
energy resolution such as with
\begin{quote}
{\tt
int i; \\
for(i=5;i<20;i++) \\
\{ \\    
\hspace*{1cm} glbClearExperimentList(); \\
\hspace*{1cm} glbDefineAEDLVariable("myres",0.01*i); \\
\hspace*{1cm} glbInitExperiment(...); \\
\\
\hspace*{1cm} /* do something */ \\
\}
}
\end{quote}
Note that one does not have to re-initialize the oscillation
parameter vectors every time within the loop as long as the
number of experiments does not change. The counterpart of that
function is\footnote{Supported by version 3.1.7 and higher.}
\begin{function}
\GLBNS{GetAEDLVariable}
{\tt double glbGetAEDLVariable(const char* name)}
returns the value of the \AEDL\ variable {\tt name}.
\end{function}
